### 2013-09-22 fig_mr_arfi_path_axes.tex
updated figures for correlation analyses and removed image comparisons to path axes

\begin{figure}[htb!]
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\linewidth]{figs/Lateral-to-Lateral} &
\includegraphics[width=0.3\linewidth]{figs/Anterior-to-Posterior} &
\includegraphics[width=0.3\linewidth]{figs/Apex-to-Base} \\
(a) & (b) & (c) \\
\end{tabular}
\caption{Measurements of the prostate dimensions along the three standard
anatomic axes: lateral-to-lateral (a), anterior-to-posterior (b) and
apex-to-base (c).  The correlation between the imaging axis measurements and
pathology was performed for each orientation.  The black dashed-line represents
the projection of perfectly-correlated measurements between imaging and
patholoy.  Notice that there is no correlation between imaging and pathology in
the lateral-to-lateral and anterior-to-posterior axes, with a general
over-estimation of the lateral-to-lateral axis in the imaging.  The MR
estimation of the apex-to-base dimension showed moderate correlation with
pathology, with the ARFI image apex-to-base approximation having an overall
underestimation in this orientation.}
\label{fig:mr_arfi_path_axes} 
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\begin{tabular}{ccc}
%\includegraphics[width=0.3\linewidth]{figs/Lateral-to-Lateral} &
%\includegraphics[width=0.3\linewidth]{figs/Anterior-to-Posterior} &
%\includegraphics[width=0.3\linewidth]{figs/Apex-to-Base} \\
%(a) & (b) & (c) \\
\includegraphics[width=0.3\linewidth]{figs/Imaging_Lateral-to-Lateral} &
\includegraphics[width=0.3\linewidth]{figs/Imaging_Anterior-to-Posterior} &
\includegraphics[width=0.3\linewidth]{figs/Imaging_Apex-to-Base} \\
(a) & (b) & (c) \\
%(d) & (e) & (f) \\
\end{tabular}
\caption{Measurements of the prostate dimensions along the three standard
    anatomic axes: lateral-to-lateral (a), anterior-to-posterior (b) and
    apex-to-base (c).  The correlation between the MR and ARFI imaging axis
    measurements was performed in each orientation for the total gland (black
    crosses) and central gland (red circles).  The black dashed-line represents
    the projection of perfectly-correlated measurements between imaging and
    patholoy.  The over-/under-estimation of each imaging modality relative to
    gross pathology and each other is summarized in
    Table~\ref{tab:mr_arfi_axes_error}.} 
\label{fig:mr_arfi_path_axes}
\end{figure}
